Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-05 edubots_surveys.Rnw
Updating the Introduction section
Added the first paragraph in the introduction section

The key findings of this study shed the light on educators’ preference to use messaging applications that their institutions support.  Technology adoption literature often focus on users’ perceptions of the technology’s usefulness and ease of use as important prerequisites for successful adoption and utilization. Nevertheless, in higher education, institutions’ role in integrating these tools to their educational systems can improve the uptake of these applications and shape the social and educational experiences of their students.  This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .  
Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.  Teachers tend to adopt technologies supported by their institutions.  This could be to ensure that their universities can oversee their efforts in supporting their students during the learning process.  Another reason could be their familiarity with the technology provided by their institutions. On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.  It is worth noting that peer support and collaboration is inseparable from learning \cite{ timmis2012constant } and correlates positively with higher retention in higher education \cite{ o2014front }.  Therefore, both perspectives are complementary and play different roles in promoting the learning process.
%This section is repeated
%\section*{Acknowledgements}

>>>>

The key findings of this study shed the light on educators’ preference to use messaging applications that their institutions support.  Technology adoption literature often focus on users’ perceptions of the technology’s usefulness and ease of use as important prerequisites for successful adoption and utilization. Nevertheless, in higher education, institutions’ role in integrating these tools to their educational systems can improve the uptake of these applications and shape the social and educational experiences of their students.  This integration, to be fruitful, institutions have to ensure that these messaging applications not only are GDPR compliant to keep students’ data secure but also should provide IT support to all stakeholders who use the applications .  
Moreover, this study clarifies the differences between the teachers’ perspectives and/or intentions and that of their students when using the messaging applications in higher education.  Teachers tend to adopt technologies supported by their institutions.  This could be to ensure that their universities can oversee their efforts in supporting their students during the learning process.  Another reason could be their familiarity with the technology provided by their institutions. On the other hand, students use the non-institution messaging applications to form informal discussion groups with their peers.  It is worth noting that peer support and collaboration is inseparable from learning \cite{timmis2012constant} and correlates positively with higher retention in higher education \cite{o2014front}.  Therefore, both perspectives are complementary and play different roles in promoting the learning process.
%This section is repeated
%\section*{Acknowledgements}
